### 2015-12-30 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to CAFS report

The second water and CAFs comparison was to examine 5 replicate tests for a straight stream in the mid-position, Fig.~\ref{fig:CAFS_Water_Comp_SS_mid}. The same analysis was performed for this configuration. These results also indicate that there is

@@

Smoke is Fuel. A ventilation limited (fuel rich) condition had developed prior to the failure of the window. Oxygen depleted combustion products, containing carbon dioxide, carbon monoxide and
unburned hydrocarbons filled the rooms of the structure. Once the window failed, the fresh air provided the oxygen needed to sustain the transition through flashover, which caused a significant increase in heat release rate.

Venting does not always equal cooling. In this experiment, post ventilation temperatures and heat fluxes all increased, due to the ventilation induced flashover. Fire induced flows. Velocities within the structure exceeded 5 m/s (11 mph), just due to the fire growth and the flow path that was set-up between the window opening and the corridor vent. Avoid the flow path. The directional nature of the fire gas flow was demonstrated with thermal conditions, both temperature and heat flux, which were twice as high in the ``flow'' portion of the
corridor as opposed to the ``static" portion of the corridor. Thermal conditions in the flow path were not consistent with firefighter survival.

The fuel load in the structure was the same for all of the experiments. Each of these experiments demonstrated a rapid transition to untenable conditions in the corridor, even for a firefighter in full PPE.

The externally applied water streams were implemented in three different ways; a fog stream across the face of the window opening, a fog stream into the window opening, and a solid water stream into the window opening.

These experiments demonstrated the ``extreme'' thermal conditions that can be generated by a ``simple room and contents'' fire and how these conditions can be extended along a flow path within a structure. The experiments also provided potential guidance for firefighters as a part of a fire size up and approach to the room of fire origin: note wind conditions in the area of the fire, look for ``pulsing flames'', examine smoke conditions around closed doors in the potential flow path, and maintain control of doors in the flow path.

Further research in actual buildings is required to fully understand the ability of firefighters to implement these tactics, to examine the thermal conditions throughout the structure such as in stairways, and to examine the interaction of these tactics with building ventilation strategies both natural and with positive pressure ventilation.

>>>>

The second water and CAFs comparison was to examine 5 replicate tests for a straight stream in the mid-position, Fig.~\ref{fig:CAFS_Water_Comp_SS_mid}. The same analysis was performed for this configuration. These results also illustrate the inability to discern which suppression agent is more or less effective at gas cooling.

@@
